О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Cosmetic edits

For every integer $n\geq 3$ Solymosi~\cite{solymosi2003note} gives a construction of facher planar integral point set $M$
such as $|M| = n$ and for some $M_1, M_2 \in M$ holds $|M_1 - M_2| = 2$.
The construted set has both odd and even distances.

>>>>

For every integer $n\geq 3$ Solymosi~\cite{solymosi2003note} gives a construction of a facher integral point set
$M\in\mathfrak{M}(2,n)$
such that equality $|M_1 - M_2| = 2$ holds for some $M_1, M_2 \in M$.
The constructed set has both odd and even distances.
